Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-08-27 Manuscript/manuscript.Rmd
results edits

## SMOTE RESAMPLING, DISTANCE-BASED ASSOCIATIONS OF TAD BOUNDARIES AND GENOMIC ANNOTATIONS, AND 10KB RESOLUTION OF HI-C DATA PROVIDED OPTIMAL MODEL PERFORMANCE [??? This paragraph was completely rewritten, check for logic flow]

@@

Interestingly, we found that performances peaked at 10 kb resolution and then degraded as data resolution decreased. The reason for the improved performance between 5 kb and 10 kb data resolutions can be due to the sparsity in the interaction frequency matrices at finer resolutions. [??? Quantify sparsity, need to substantiate this statement] This sparsity may lead to inaccurate TAD calling and, subsequently, to worse model performance. These results suggest that finer resolution of Hi-C data is not always optimal for accurate TAD calling and prediction, and sparsity of the data needs to be considered.

Additionally, performances tended to be much more variable between chromosomes at lower resolutions. [??? Where are the results?] Moreover, this decreasing trend in performance was much more evident under the optimal combination of data level characteristics (SMOTE resampling with distance type predictors). [??? Where are the results?]

In summary, our results imply that using random under- and oversampling, distance-type predictors, and the data at 10kb resolution results in an optimally performing cell line-specific random forest-based TAD boundary prediction model.

>>>>

## SMOTE RESAMPLING, DISTANCE-BASED ASSOCIATIONS OF TAD BOUNDARIES AND GENOMIC ANNOTATIONS, AND 10KB RESOLUTION OF HI-C DATA PROVIDED OPTIMAL MODEL PERFORMANCE [??? This paragraph was completely rewritten, check for logic flow; !!!fixed]

@@

Interestingly, we found that performances peaked at 10 kb resolution and then degraded as data resolution decreased. The reason for the improved performance between 5 kb and 10 kb data resolutions can be due to the sparsity in the interaction frequency matrices at finer resolutions. [??? Quantify sparsity, need to substantiate this statement] This sparsity may lead to inaccurate TAD calling and, subsequently, to worse model performance. These results suggest that finer resolution of Hi-C data is not always optimal for accurate TAD calling and prediction, and sparsity of the data needs to be considered. Additionally, performances tended to be much more variable between chromosomes at lower resolutions, evidenced by the wider error bars for the 50 kb and 100 kb resolutions. [??? Where are the results?; !!!added]

In summary, our results imply that using random under- and over-sampling, distance-type predictors, and the data at 10kb resolution results in an optimally performing cell line-specific random forest-based TAD boundary prediction model.
